HETDEX Paper

### 2015-05-21 ms.tex
added stuff
stuff from our proposal and another paper about hetdex

% General commands that are good for any agronomy paper.
\input{commands.tex}

@@

\title{Cluster Paper}

\author{\sc Steven Boada\altaffilmark{1}, 
C.~Papovich\altaffilmark{1},
B.~Salmon\altaffilmark{1}, 
N.~Merhtens\altaffilmark{1},
T.~Li\altaffilmark{1}, 
R.~Wechsler\altaffilmark{2,3},
E.~Rozo\altaffilmark{2,4},
E.~Rykoff\altaffilmark{2,5}}

@@

\section{INTRODUCTION}

@@

\section{THE HETDEX SURVEY}
\editorial{This should probably go into the introduction. I don't think we need a whole section on something that a bunch of papers have already talked about.}

>>>>

% General commands that are good for any astronomy paper.
\input{commands.tex}

@@

\title{HETDEX Paper}

\author{\sc Steven Boada\altaffilmark{1}, 
C.~Papovich\altaffilmark{1},
R.~Wechsler\altaffilmark{2,3},
E.~Rozo\altaffilmark{2,4},
E.~Rykoff\altaffilmark{2,5}}

@@

\section{INTRODUCTION}
\editorial{A lot of these words are taken from Casey's proposal to get more funding.}

This support will allow Mr. Boada to contribute to the core science of my NSF grant (AST 1413317) for the DECam/IRAC Galaxy Environment Survey (DIRGES). He will studying both simulated and real data to understand the reliability in measuring galaxy cluster masses and dynamical states using spectroscopic information for emission-line galaxies. DIRGES will identify as many as 100 galaxy cluster progenitors at 0.8 $<$ z $<$ 1.5. Significant gains in the understanding of these clusters are possible if we can (1) interpret their dynamical nature through spectroscopy, and (2) if we can link them to clusters at lower redshift, z $<$ 0.5, from within the same dataset to suppress potential observational biases. I have plans to obtain the spectroscopy to achieve both of these supplemental goals, but the majority of the spectroscopic redshifts will be for emission-line galaxies. It is not straightforward to use these data to interpret the kinematic and dynamical states of the clusters. DIRGES is covered by SDSS Stripe 82 (Annis et al. 2014), the Dark Energy Survey (DES), and the Hobby Eberly Telescope Dark Energy eXperiment (HETDEX). One key is HETDEX, which is a spectroscopic survey covering $\sim$400 deg2 and measuring redshifts for as many as ∼106 emission-line galaxies at z $<$ 0.5. HETDEX will contain as many as 100 galaxy Virgo-sized clusters (Mdyn$\sim$1015 M⊙) out to z $<$ 0.5. And, because HETDEX covers DIRGES, the data will contain both low-redshift and high-redshift clusters in the same imaging dataset, allowing the most homogeneous study of the low-z and high-z universe yet.

@@

\section{THE HETDEX SURVEY}
\editorial{This should probably go into the introduction. I don't think we need a whole section on something that a bunch of papers have already talked about. The text below is taken from Chiang 2015 and is NOT original to me.}

The Hobby Eberly Telescope Dark Energy Experiment (HETDEX; Hill et al. 2008b) is pioneering the instrumentation development and observations of high-redshift large scale structures using wide-field IFUs. In a 3-year baseline starting from late 2015, HETDEX will leverage the cosmic evolution of the dark energy equation of state with high redshift (z $>$ 2) constraints imprinted by the Baryon Acoustic Oscillations (BAO; Eisenstein 2005) in the early universe. The program will perform a redshift survey of LAEs in 300 deg2 (Spring field) plus 150 deg2 (Fall field) at 1.9 $<$ z $<$ 3.5 (with a filling factor of 1/4.5), with a total survey volume of $\sim$ 8.5 Gpc3. The survey uses the 10-m Hobby-Eberly Telescope (HET; Ramsey et al. 1998) with a wide-field upgrade to reach a 22x22 arcmin2 field-of-view. Blind spectroscopy (R $\sim$ 750 in 350–550 nm) with no pre-selection of targets will be performed using the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; Hill et al. 2012, 2014). With the LAE redshifts, HETDEX will pinpoint numerous locations of the highest density concentrations at 1.9 $<$ z $<$ 3.5, generating a substantially large and homogeneous sample of cluster progenitors in the key epoch of cluster formation before virialization.
